\section*{Abstract}
	
Measurements of the radio sky at frequencies below \SI{\sim {100}}{\mega \hertz} have the potential to unlock a new observational window into the universe’s history. These observations allow us to probe even earlier epochs of the universe’s history and lay the groundwork for eventually exploring the cosmic “dark ages”. \attention{[This preamble should be updated slightly to include the cosmic dawn science too, not just the dark ages, because you're going to introduce PRIZM below.]} There is minimal knowledge about the radio sky below \SI{30}{\mega \hertz}. The lowest measured frequency of the radio sky dates from the 1960s when Grote Reber mapped a portion of the sky at \SI{\sim 2}{\mega \hertz} using a 192-element dipole array with $\sim$5 \degree resolution. This brief glimpse of low-frequency Galactic emission was made possible partly by an unusually deep solar minimum.

This thesis presents the Array of Long Baseline Antennas for Taking Radio Observations from the Sub-Antarctic (\albatros) and upgrades to Probing Radio Intensity at high-Z from Marion (\prizm) subsystems. The two experiments are installed in Marion Island located in the southern Indian Ocean. \st{In 2019 I played a leading role in} \attention{[strong phrasing like what you wrote is better placed in an application or a proposal, rather than a thesis or article] This thesis focuses on} the deployment of the first autonomous \albatros\ station\attention{, which took place in 2019}. Prior to the deployment of the autonomous station, the two-element pathfinder was installed to assess the observable frequencies from Marion below \SI{30}{\mega \hertz}. The final ALBATROS array will consist of ten autonomous antenna stations separated by maximum baseline lengths of \SI{\sim {20}}{km}. \st{In preparation for the 2020 deployement I designed a} \attention{This thesis also presents the design of a} new second stage electronics enclosure \st{using Autodesk Inventor Professional 2018} \attention{[this is too much detail for an abstract]} and \st{assisted with further revision of the components that fit inside the enclosure} \attention{and other subsystem upgrades for \prizm\ that were intended for the 2020 deployment}. \st{The enclosure was fabricated and the sheet metal parts fitted together as designed, all the components were installed in the enclosures and fit to the mounting holes that were already in place. COVID-19 lockdowns happened before dry-runs could be perfomed.} \attention{[Too much detail for an abstract.  Replace with a sentence giving a bigger picture description of the motivation behind the upgrades.]}

Preliminary observations from the \attention{\albatros} pathfinder installed in April 2018 show discernible interferometric fringes from the sky visible down to \SI{\sim 10}{\mega \hertz} without any data processing or cuts. The first fully autonomous antenna station was deployed in April 2019, configured to record baseband data, and with power supplied by solar panels. \attention{[End with a sentence commenting on the performance of the autonomous antenna station.]}

