\section*{Acknowledgements}

Throughout my life, I have been blessed, highly favored, and fortunate to have been granted several opportunities that have led me to undertake this research thesis. Thank you to the thousands of people in the universe who have provided me with the foundation, environment, safety, health, support, service, financial well-being, love, joy, knowledge, kindness, calmness, and happiness to produce this work.

My sincerest gratitude goes to Profs. Cynthia Chiang and Jonathan Sievers for giving me a platform to realize and prove my strengths and capabilities. The unusual path that I took in joining radio astronomy research is a lifetime opportunity that has opened doors for me and my career. Words can never express my gratitude for the life skills, adventurous experiences, and independence that I have gained through you. It has indeed been a great ride!

I want to thank Prof. Matt Hilton and Dr. Ilya Sinayskiy. During the years that I have spent at the University of KwaZulu Natal, you have had a remarkable impact on my academic and career growth and recognition. 

A special thanks to the National Astrophysics and Space Science Programme for funding my studies since 2018. This thesis's completion would not have been possible without collaborative efforts from the McGill University, \prizm\ and \albatros\ teams, and the H1-225 lab mates. 

All my friends and acquaintances who have been pushing me to do and be the best I can, I thank you all for therapeutic sessions, academic, financial, personal growth, empathy, motivation, and outings.

My family's prayers throughout this journey of life have been my greatest pillar of strength. The support I receive from you, Mongi is immeasurable; thank you for always having my back. \\[4 cm]


\begin{center}
	\emph{"Dear God, thank you...!"}
\end{center}


